All Locoweed Analysis Report

### 2024-03-05 aboutme.qmd
Update website 4/5/24

```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
  <meta charset="UTF-8">
  <meta name="viewport" content="width=device-width, initial-scale=1.0">
  <title>Image Gallery</title>
  <style>
    .gallery {
      display: grid;
      grid-template-columns: repeat(auto-fill, minmax(200px, 1fr));
      grid-gap: 10px;
    }

    .gallery img {
      width: 100%;
      height: auto;
      cursor: pointer;
      transition: transform 0.3s ease;
    }

    .gallery img:hover {
      transform: scale(1.05); /* Slightly increase size on hover */
    }

    .expanded-container {
      position: fixed;
      top: 0;
      left: 0;
      width: 100%;
      height: 100%;
      background-color: rgba(0, 0, 0, 0.8); /* Semi-transparent background */
      display: none; /* Initially hidden */
      justify-content: center;
      align-items: center;
      z-index: 9999;
    }

@@

  function navigateGallery(event) {
    // Calculate the click position relative to the expanded image
    var clickX = event.pageX - event.target.offsetLeft;
    var imageWidth = event.target.offsetWidth;

>>>>

```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
  <meta charset="UTF-8">
  <meta name="viewport" content="width=device-width, initial-scale=1.0">
  <title>Image Gallery</title>
  <style>
    .gallery {
      display: grid;
      grid-template-columns: repeat(auto-fill, minmax(200px, 1fr));
      grid-gap: 10px;
    }
    .gallery img {
      width: 100%;
      height: auto;
      cursor: pointer;
      transition: transform 0.3s ease;
    }
    .gallery img:hover {
      transform: scale(1.05); /* Slightly increase size on hover */
    }
    .expanded-container {
      position: fixed;
      top: 0;
      left: 0;
      width: 100%;
      height: 100%;
      background-color: rgba(0, 0, 0, 0.8); /* Semi-transparent background */
      display: none; /* Initially hidden */
      justify-content: center;
      align-items: center;
      z-index: 9999;
    }

@@

  function navigateGallery(event) {
    // Calculate the click position relative to the expanded image
    var clickX = event.pageX - event.target.getBoundingClientRect().left;
    var imageWidth = event.target.offsetWidth;

### 2024-03-05 bugs.qmd
Update website 4/5/24

---
title: "bug pictures"
filters:
  - lightbox
lightbox: auto
---

![Bug pic 1](img/bugs/IMG_1664.JPG){group="my-gallery"}
![Bug pic 2](img/bugs/IMG_1678.JPG){group="my-gallery"}

<figure>
  <img src="img/bugs/IMG_1664.JPG" alt="Montana State University" 
  width = 200" height = "200">
</figure>

>>>>

---
title: "Bugs"
output: html_document
---

```{r  echo = F, eval = F}
# Set the directory path
directory_path <- "img/bugs"

# List all the files in the directory
file_names <- list.files(directory_path)

# Exclude files with .zip extension
file_names <- file_names[!grepl("\\.zip$", file_names)]

# Initialize an empty character vector to store the HTML code
html_code <- "<div class=\"gallery\">\n"

# Loop through each file name and generate HTML code
for (i in seq_along(file_names)) {
  # Generate the HTML code for each image
  image_html <- paste0('<img src="', directory_path, "/", file_names[i], '" alt="Image ', i, '" onclick="expandImage(this)">\n')

  # Append the generated HTML code to the existing code
  html_code <- paste(html_code, image_html, sep = "")
}

# Close the gallery div
html_code <- paste(html_code, "</div>\n<div class=\"expanded-container\" onclick=\"closeExpanded()\">\n  <img class=\"expanded\" id=\"expanded-image\" onclick=\"navigateGallery(event)\">\n</div>", sep = "")

# Print the final HTML code
cat(html_code)
```

```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
  <meta charset="UTF-8">
  <meta name="viewport" content="width=device-width, initial-scale=1.0">
  <title>Image Gallery</title>
  <style>
    .gallery {
      display: grid;
      grid-template-columns: repeat(auto-fill, minmax(150px, 1fr));
      grid-gap: 10px;
    }
    .gallery img {
      width: 100%;
      height: 100%;
      object-fit: cover; /* Ensure images cover the entire space */
      cursor: pointer;
      transition: transform 0.3s ease;
    }
    .gallery img:hover {
      transform: scale(1.05); /* Slightly increase size on hover */
    }
    .expanded-container {
      position: fixed;
      top: 0;
      left: 0;
      width: 100%;
      height: 100%;
      background-color: rgba(0, 0, 0, 0.8); /* Semi-transparent background */
      display: none; /* Initially hidden */
      justify-content: center;
      align-items: center;
      z-index: 9999;
    }

    .expanded {
      max-width: 80%;
      max-height: 80%;
      cursor: pointer;
    }
  </style>
</head>
<body>

<div class="gallery">
<img src="img/bugs/blueflowers.JPG" alt="Image 1" onclick="expandImage(this)">
<img src="img/bugs/brownmoth.JPG" alt="Image 2" onclick="expandImage(this)">
<img src="img/bugs/brownred-butterfly.JPG" alt="Image 3" onclick="expandImage(this)">
<img src="img/bugs/butterfly-purpleflower.JPG" alt="Image 4" onclick="expandImage(this)">
<img src="img/bugs/loco-bee.JPG" alt="Image 5" onclick="expandImage(this)">
</div>
<div class="expanded-container" onclick="closeExpanded()">
  <img class="expanded" id="expanded-image" onclick="navigateGallery(event)">
</div>

<script>
  var currentImageIndex = 0;
  var galleryImages = document.querySelectorAll('.gallery img');

  function expandImage(img) {
    currentImageIndex = Array.from(galleryImages).indexOf(img);
    document.getElementById('expanded-image').src = img.src;
    document.querySelector('.expanded-container').style.display = 'flex';
  }

  function closeExpanded() {
    document.querySelector('.expanded-container').style.display = 'none';
  }

  function navigateGallery(event) {
    // Calculate the click position relative to the expanded image
    var clickX = event.pageX - event.target.getBoundingClientRect().left;
    var imageWidth = event.target.offsetWidth;

    // Determine if the click was on the left or right side of the image
    if (clickX < imageWidth / 2) {
      // Clicked on the left side: navigate to the previous image
      currentImageIndex = (currentImageIndex - 1 + galleryImages.length) % galleryImages.length;
    } else {
      // Clicked on the right side: navigate to the next image
      currentImageIndex = (currentImageIndex + 1) % galleryImages.length;
    }

    // Update the expanded image source
    document.getElementById('expanded-image').src = galleryImages[currentImageIndex].src;
  }
</script>

</body>
</html>

```

<br>
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Button</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
</style>
</head>
<body>

<!-- Button to download the file -->
<a href="img/bugs/Jackson-Bug-Pics.zip" download="Jackson Bug Pictures">
  <button class="button">Download All Pictures</button>
</a>

</body>
</html>

```

```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Image Crop Example</title>
<style>
  .image-container {
    width: 300px; /* Set the width of the container */
    height: 200px; /* Set the height of the container */
    overflow: hidden; /* Hide any overflowing content */
  }
  .cropped-image {
    width: 100%; /* Set the width of the image to fill the container */
    height: auto; /* Automatically adjust the height to maintain aspect ratio */
    object-fit: cover; /* Crop the image to cover the container */
  }
</style>
</head>
<body>

<div class="image-container">
  <img class="cropped-image" src="img/bugs/loco-bee.png" alt="Cropped Image">
</div>

</body>
</html>

```

### 2024-03-05 deadhorse.qmd
Update website 4/5/24

::: {style="display: grid;grid-template-columns: repeat(auto-fill, minmax(200px, 1fr));grid-gap: 1em;"}
```{r get images, echo = F, results = 'asis'}
image_files <- list.files("img/deadhorse", pattern = ".JPG|.png|.gif|.jpg|.jpeg", full.names = TRUE)

for (file in image_files) {
  cat("![](",file, ")\n  \n")
}
```
:::

>>>>

```{r eval = F, echo = F}
# Set the directory path
directory_path <- "img/deadhorse"

# List all the files in the directory
file_names <- list.files(directory_path)

# Exclude files with .zip extension
file_names <- file_names[!grepl("\\.zip$", file_names)]

# Initialize an empty character vector to store the HTML code
html_code <- "<div class=\"gallery\">\n"

# Loop through each file name and generate HTML code
for (i in seq_along(file_names)) {
  # Generate the HTML code for each image
  image_html <- paste0('<img src="', directory_path, "/", file_names[i], '" alt="Image ', i, '" onclick="expandImage(this)">\n')

  # Append the generated HTML code to the existing code
  html_code <- paste(html_code, image_html, sep = "")
}

# Close the gallery div
html_code <- paste(html_code, "</div>\n<div class=\"expanded-container\" onclick=\"closeExpanded()\">\n  <img class=\"expanded\" id=\"expanded-image\" onclick=\"navigateGallery(event)\">\n</div>", sep = "")

# Print the final HTML code
cat(html_code)
```

```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
  <meta charset="UTF-8">
  <meta name="viewport" content="width=device-width, initial-scale=1.0">
  <title>Image Gallery</title>
  <style>
    .gallery {
      display: grid;
      grid-template-columns: repeat(auto-fill, minmax(150px, 1fr));
      grid-gap: 10px;
    }
    .gallery img {
      width: 150px;
      height: 150px;
      object-fit: cover; /* Ensure images cover the entire space */
      cursor: pointer;
      transition: transform 0.3s ease;
    }
    .gallery img:hover {
      transform: scale(1.05); /* Slightly increase size on hover */
    }
    .expanded-container {
      position: fixed;
      top: 0;
      left: 0;
      width: 100%;
      height: 100%;
      background-color: rgba(0, 0, 0, 0.8); /* Semi-transparent background */
      display: none; /* Initially hidden */
      justify-content: center;
      align-items: center;
      z-index: 9999;
    }

    .expanded {
      max-width: 80%;
      max-height: 80%;
      cursor: pointer;
    }
  </style>
</head>
<body>

<div class="gallery">
<img src="img/deadhorse/deadhorse-top.JPG" alt="Image 1" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_0012.JPG" alt="Image 2" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_0016.JPG" alt="Image 3" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_0026.JPG" alt="Image 4" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6044.jpeg" alt="Image 5" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6050.jpeg" alt="Image 6" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6058.jpeg" alt="Image 7" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6061.jpeg" alt="Image 8" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6062.jpeg" alt="Image 9" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6067.jpeg" alt="Image 10" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6071.jpeg" alt="Image 11" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6078.jpeg" alt="Image 12" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6079.jpeg" alt="Image 13" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6080.jpeg" alt="Image 14" onclick="expandImage(this)">
<img src="img/deadhorse/IMG_6192.HEIC" alt="Image 15" onclick="expandImage(this)">
</div>
<div class="expanded-container" onclick="closeExpanded()">
  <img class="expanded" id="expanded-image" onclick="navigateGallery(event)">
</div>

<script>
  var currentImageIndex = 0;
  var galleryImages = document.querySelectorAll('.gallery img');

  function expandImage(img) {
    currentImageIndex = Array.from(galleryImages).indexOf(img);
    document.getElementById('expanded-image').src = img.src;
    document.querySelector('.expanded-container').style.display = 'flex';
  }

  function closeExpanded() {
    document.querySelector('.expanded-container').style.display = 'none';
  }

  function navigateGallery(event) {
    // Calculate the click position relative to the expanded image
    var clickX = event.pageX - event.target.getBoundingClientRect().left;
    var imageWidth = event.target.offsetWidth;

    // Determine if the click was on the left or right side of the image
    if (clickX < imageWidth / 2) {
      // Clicked on the left side: navigate to the previous image
      currentImageIndex = (currentImageIndex - 1 + galleryImages.length) % galleryImages.length;
    } else {
      // Clicked on the right side: navigate to the next image
      currentImageIndex = (currentImageIndex + 1) % galleryImages.length;
    }

    // Update the expanded image source
    document.getElementById('expanded-image').src = galleryImages[currentImageIndex].src;
  }

  // Add event listeners to the left and right sides of the expanded image for navigation
  document.querySelector('.expanded').addEventListener('click', function(event) {
    navigateGallery(event);
  });
</script>

</body>
</html>

```
<br>
```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Download File Button</title>
<style>
/* Button styling */
.button {
  background-color: #2068DC; /* Header of website color (blue) */
  border: none;
  color: white;
  padding: 15px 32px;
  text-align: center;
  text-decoration: none;
  display: inline-block;
  font-size: 16px;
  margin: 4px 2px;
  cursor: pointer;
  border-radius: 8px;
}
.button:hover {
  background-color: #3F91FB; /* Sky blue */
}
</style>
</head>
<body>

<!-- Button to download the file -->
<a href="img/deadhorse/DeadhorseUltra2023.zip" download="DeadhorseUltra2023">
  <button class="button">Download All Pictures</button>
</a>

</body>
</html>

```

### 2024-03-05 field_report.qmd
Update website 4/5/24

---
title: "MT Field Site Analysis Report"
author: "Jackson Strand"
date: "`r Sys.Date()`"
output: 
  html_document:
    self_contained: yes
    include:
    keep_md: true
    theme: cosmo
    toc: true
    toc_float: true
    toc_title: "Table of Contents"
    toc_collapsed: false
    toc_depth: 4
    # number_sections: true
editor_options: 
  chunk_output_type: console
---
```{r library, echo = F, message = F, warning = F}
library(tidyverse)
library(readxl)
library(ggplot2)
library(kableExtra)
library(plotly)
```
```{r column.order, echo = F}
column.order <- c("distance", "collection", "p.inf", 
                  "p.cut", "p.par", "poten")

@@

![North Road, Big Sandy, MT (2023)](https://github.com/jstrand894/Website/blob/main/nnns-min.png?raw=true)

@@

![Gardiner Road, Big Sandy, MT (2023)](https://github.com/jstrand894/Website/blob/main/gardiner%20road-min.png?raw=true)

@@

![Harvest & Sunset Road Instersection, Big Sandy, MT (2023)](https://github.com/jstrand894/Website/blob/main/harvest%20road-min.png?raw=true)

@@

![Kolin Road, Moccasin, MT (2023)](https://github.com/jstrand894/Website/blob/main/kolin%20road-min.png?raw=true)

```{r K data table, echo = F}
k.table <-
stubble.brome %>%
  filter(location %in% c("k"),
         year == "2023") %>%
  dplyr::select(location, distance, collection, year, type, mean) %>%
  mutate(mean = round_based_on_size(mean)) %>%
  mutate_at(vars(location, distance, collection, year, type), as.factor) %>%
  pivot_wider(names_from = type,
              values_from = mean,
              values_fn = list(mean = mean)) %>%
  arrange(distance) %>%
  ungroup() %>%
  dplyr::select(-year)

>>>>

---
title: "MT Field Site Analysis Report"
author: "Jackson Strand"
date: "`r Sys.Date()`"
output: 
  quarto::quarto_html:
    layout: sidebar
    theme: cosmo
    toc: true
    toc_float: true
    toc_title: "Table of Contents"
    toc_collapsed: false
    toc_depth: 4
    # number_sections: true
editor_options: 
  chunk_output_type: console
---
```{r library, echo = F, message = F, warning = F}
library(tidyverse)
library(readxl)
library(ggplot2)
library(kableExtra)
library(plotly)
```
```{r column.order, echo = F}
column.order <- c("distance", "collection", "p.inf", 
                  "p.cut", "p.par", "poten")

@@

```{=html}
<html lang="en">
<head>
  <meta charset="UTF-8">
  <meta name="viewport" content="width=device-width, initial-scale=1.0">
  <title>Centered Image Expand</title>
  <style>
    body, html {
      margin: 0;
      padding: 0;
      height: 100%;
    }
    .container {
      display: flex;
      justify-content: left;
      align-items: left;
      height: auto;
    }
    .image {
      max-width: 50%;
      max-height: 80vh;
      cursor: pointer;
      transition: transform 0.3s ease;
    }
    .image:hover {
      transform: scale(1.05); /* Slightly increase size on hover */
    }
    .image.expanded {
      transform: scale(3); /* Scale up when expanded */
      z-index: 9999; /* Ensure expanded image is on top */
      position: fixed;
      top: 50%;
      left: 50%;
      max-height: 80%;
      max-width: 80%;
      transform: translate(-50%, -50%); /* Center expanded image */
    }
    .overlay {
      position: fixed;
      top: 0;
      left: 0;
      width: 100%;
      height: 100%;
      background-color: rgba(0, 0, 0, 0.5); /* Semi-transparent dark background */
      z-index: 9998; /* Ensure overlay is behind the expanded image */
      display: none; /* Initially hidden */
    }
    .image.expanded + .overlay {
      display: block; /* Show overlay when image is expanded */
    }
  </style>
</head>
<body>

<div class="container">
  <img class="image" src="img/field-sites/nnns.png" alt="Image" onclick="expandImage(this)">
  <div class="overlay" onclick="closeExpandedImage()"></div> <!-- Overlay element -->
</div>

<script>
  function expandImage(element) {
    element.classList.toggle('expanded');
    document.querySelector('.overlay').classList.toggle('expanded');
  }

  function closeExpandedImage() {
    var image = document.querySelector('.image');
    image.classList.remove('expanded');
    document.querySelector('.overlay').classList.remove('expanded');
  }
</script>

</body>
</html>
```

<!-- ![North Road, Big Sandy, MT (2023)](https://github.com/jstrand894/Website/blob/main/nnns-min.png?raw=true) -->

@@

```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
  <meta charset="UTF-8">
  <meta name="viewport" content="width=device-width, initial-scale=1.0">
  <title>Centered Image Expand</title>
  <style>
    body, html {
      margin: 0;
      padding: 0;
      height: 100%;
    }
    .container {
      display: flex;
      justify-content: left;
      align-items: left;
      height: auto;
    }
    .image {
      max-width: 50%;
      max-height: 80vh;
      cursor: pointer;;
      transition: transform 0.3s ease;
    }
    .image:hover {
      transform: scale(1.05); /* Slightly increase size on hover */
    }
    .image.expanded {
      transform: scale(3); /* Scale up when expanded */
      z-index: 9999; /* Ensure expanded image is on top */
      position: fixed;
      top: 50%;
      left: 50%;
      max-height: 80%;
      max-width: 80%;
      transform: translate(-50%, -50%); /* Center expanded image */
    }
    .overlay {
      position: fixed;
      top: 0;
      left: 0;
      width: 100%;
      height: 100%;
      background-color: rgba(0, 0, 0, 0.5); /* Semi-transparent dark background */
      z-index: 9998; /* Ensure overlay is behind the expanded image */
      display: none; /* Initially hidden */
    }
    .image.expanded + .overlay {
      display: block; /* Show overlay when image is expanded */
    }
  </style>
</head>
<body>

<div class="container">
  <img class="image" src="img/field-sites/gardiner.png" alt="Image" onclick="expandImage(this)">
  <div class="overlay" onclick="closeExpandedImage()"></div> <!-- Overlay element -->
</div>

<script>
  function expandImage(element) {
    element.classList.toggle('expanded');
    document.querySelector('.overlay').classList.toggle('expanded');
  }

  function closeExpandedImage() {
    var image = document.querySelector('.image');
    image.classList.remove('expanded');
    document.querySelector('.overlay').classList.remove('expanded');
  }
</script>

</body>
</html>
```

<!-- ![Gardiner Road, Big Sandy, MT (2023)](https://github.com/jstrand894/Website/blob/main/gardiner%20road-min.png?raw=true) -->

@@

```{=html}
<html lang="en">
<head>
  <meta charset="UTF-8">
  <meta name="viewport" content="width=device-width, initial-scale=1.0">
  <title>Centered Image Expand</title>
  <style>
    body, html {
      margin: 0;
      padding: 0;
      height: 100%;
    }
    .container {
      display: flex;
      justify-content: left;
      align-items: left;
      height: auto;
    }
    .image {
      max-width: 50%;
      max-height: 80vh;
      cursor: pointer;
      transition: transform 0.3s ease;
    }
    .image:hover {
      transform: scale(1.05); /* Slightly increase size on hover */
    }
    .image.expanded {
      transform: scale(3); /* Scale up when expanded */
      z-index: 9999; /* Ensure expanded image is on top */
      position: fixed;
      top: 50%;
      left: 50%;
      max-height: 80%;
      max-width: 80%;
      transform: translate(-50%, -50%); /* Center expanded image */
    }
    .overlay {
      position: fixed;
      top: 0;
      left: 0;
      width: 100%;
      height: 100%;
      background-color: rgba(0, 0, 0, 0.5); /* Semi-transparent dark background */
      z-index: 9998; /* Ensure overlay is behind the expanded image */
      display: none; /* Initially hidden */
    }
    .image.expanded + .overlay {
      display: block; /* Show overlay when image is expanded */
    }
  </style>
</head>
<body>

<div class="container">
  <img class="image" src="img/field-sites/harvest.png" alt="Image" onclick="expandImage(this)">
  <div class="overlay" onclick="closeExpandedImage()"></div> <!-- Overlay element -->
</div>

<script>
  function expandImage(element) {
    element.classList.toggle('expanded');
    document.querySelector('.overlay').classList.toggle('expanded');
  }

  function closeExpandedImage() {
    var image = document.querySelector('.image');
    image.classList.remove('expanded');
    document.querySelector('.overlay').classList.remove('expanded');
  }
</script>

</body>
</html>
```

<!-- ![Harvest & Sunset Road Instersection, Big Sandy, MT (2023)](https://github.com/jstrand894/Website/blob/main/harvest%20road-min.png?raw=true) -->

@@

```{=html}
<html lang="en">
<head>
  <meta charset="UTF-8">
  <meta name="viewport" content="width=device-width, initial-scale=1.0">
  <title>Centered Image Expand</title>
  <style>
    body, html {
      margin: 0;
      padding: 0;
      height: 100%;
    }
    .container {
      display: flex;
      justify-content: left;
      align-items: left;
      height: auto;
    }
    .image {
      max-width: 50%;
      max-height: 80vh;
      cursor: pointer;
      transition: transform 0.3s ease;
    }
    .image:hover {
      transform: scale(1.05); /* Slightly increase size on hover */
    }
    .image.expanded {
      transform: scale(3); /* Scale up when expanded */
      z-index: 9999; /* Ensure expanded image is on top */
      position: fixed;
      top: 50%;
      left: 50%;
      max-height: 80%;
      max-width: 80%;
      transform: translate(-50%, -50%); /* Center expanded image */
    }
    .overlay {
      position: fixed;
      top: 0;
      left: 0;
      width: 100%;
      height: 100%;
      background-color: rgba(0, 0, 0, 0.5); /* Semi-transparent dark background */
      z-index: 9998; /* Ensure overlay is behind the expanded image */
      display: none; /* Initially hidden */
    }
    .image.expanded + .overlay {
      display: block; /* Show overlay when image is expanded */
    }
  </style>
</head>
<body>

<div class="container">
  <img class="image" src="img/field-sites/kolin.png" alt="Image" onclick="expandImage(this)">
  <div class="overlay" onclick="closeExpandedImage()"></div> <!-- Overlay element -->
</div>

<script>
  function expandImage(element) {
    element.classList.toggle('expanded');
    document.querySelector('.overlay').classList.toggle('expanded');
  }

  function closeExpandedImage() {
    var image = document.querySelector('.image');
    image.classList.remove('expanded');
    document.querySelector('.overlay').classList.remove('expanded');
  }
</script>

</body>
</html>
```

<!-- ![Kolin Road, Moccasin, MT (2023)](https://github.com/jstrand894/Website/blob/main/kolin%20road-min.png?raw=true) -->

```{r K data table, echo = F}
k.table <-
stubble.brome %>%
  filter(location %in% c("k"),
         year == "2023") %>%
  dplyr::select(location, distance, collection, year, type, mean) %>%
  mutate(mean = round_based_on_size(mean)) %>%
  mutate_at(vars(location, distance, collection, year, type), as.factor) %>%
  mutate(mean = mean*100) %>%
  pivot_wider(names_from = type,
              values_from = mean,
              values_fn = list(mean = mean)) %>%
  arrange(distance) %>%
  ungroup() %>%
  dplyr::select(-year)

### 2024-03-05 index.qmd
Update website 4/5/24

---
title: "Jackson Strand"
about:
  id: me
  template: marquee
  links:
    - icon: linkedin
      text: LinkedIn
      href: https://linkedin.com/in/jacksonstrand
    - icon: instagram
      text: Instagram
      href: https://www.instagram.com/jstrand894/
    - icon: github
      text: GitHub
      href: https://github.com/jstrand894 
  image: img/aboutme/deadhorse.jpeg

sidebar: false
---

:::{#me}

I am currently a Master's graduate student at Montana State University studying entomology. I live in Bozeman, MT with my wife Grace.

@@

:::

>>>>

---
about: 
  template: jolla
  id: about-block
  image: "img/aboutme/crescent.HEIC"
  links:
    - icon: linkedin
      text: LinkedIn
      href: https://linkedin.com/in/jacksonstrand
    - icon: instagram
      text: Instagram
      href: https://www.instagram.com/jstrand894/
    - icon: github
      text: GitHub
      href: https://github.com/jstrand894 
---
::: {#about-block}
:::

# Welcome to my website!

My name is Jackson Strand. I am currently a Master's graduate student at Montana State University studying entomology. I live in Bozeman, MT with my wife Grace.

@@

### 2024-03-05 locoweed-report.qmd
Update website 4/5/24

---
title: "All Locoweed Analysis Report"
author: "Jackson Strand"
date: '`r format(Sys.Date())`'
output: 
  html_document:
    toc: true
bibliography: citations/citations.bib
link-citations: true
cls: council-of-science-editors-author-date.csl
editor_options: 
  chunk_output_type: console
---

@@

# Random Forest
library(ranger)
library(MVN) # for normality test

@@

Volatiles were collected from twleve plants per day using glass volatile collection chambers (VCCs) that were 30 cm long and 4 cm in diameter. The top end of each VCC funneled into a threaded port that was 10 cm in daimter. Threaded onto the top of each VCC was an eight-port "octopus" manifold adapter. Two glass filter traps (6.35 mm diameter x 76 mm length; Analytical Research Systems, Gainesville, FL) with 30 mg of Super-Q absorbent (Alltech Associates, Deerfield, IL) were inserted into two of the adapter ports. The remaining six collection ports were sealed to prevent ambient air exchange and pressure loss. One of the traps was used to collected extraneous volatiles from the initial experiment set up for the first ten minutes, whereas the other trap was used to collect volatile compounds emanating from plants beginning ten minutes after the system was turned on. An air source was connected to the base of each collection chamber with supply from charcoal air filters. A vacuum pump was used to maintain air pressure and flow rate (humidified air at 1.0 liter/min) within the collection system. A small piece of cotton encompassed by a Teflon® guillotine was used at the base of each plant to tightly seal the base of the system and prevent external air from entering. Laboratory tape was used to seal the edges of the guillotine and prevent contamination by ambient and soil derived volatiles.

>>>>

---
title: "All Locoweed Analysis Report"
author: "Jackson Strand"
date: '`r format(Sys.Date())`'
output: 
  html_document:
    toc: true
    code_folding: hide
bibliography: citations/citations.bib
link-citations: true
cls: council-of-science-editors-author-date.csl
editor_options: 
  chunk_output_type: console
---

@@

# Random Forest
library(ranger)
library(MVN) # for normality test
```

```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
<meta charset="UTF-8">
<meta name="viewport" content="width=device-width, initial-scale=1.0">
<title>Image Cropping Example</title>
<style>
    }
    .image-container {
        width: auto; /* Set the width of the container */
        height: auto; /* Set the height of the container */
        overflow: hidden; /* Hide overflow */
    }
    .image-container img {
        width: 100%; /* Make the image fill the container horizontally */
        height: auto; /* Maintain aspect ratio */
        object-fit: cover;
        object-position: center;
    }
</style>
</head>
<body>

<div class="image-container">
    <img src="img/loco-bee-crop.JPG" alt="Your Image">
</div>

</body>
</html>

@@

```{r plant pictures, echo = F, eval = F}

# Set the directory path
directory_path <- "img/loco-plants"

# List all the files in the directory
file_names <- list.files(directory_path)

# Initialize an empty character vector to store the HTML code
html_code <- "<div class=\"gallery\">\n"

# Loop through each file name and generate HTML code
for (i in seq_along(file_names)) {
  # Generate the HTML code for each image
  image_html <- paste0('<img src="', directory_path, "/", file_names[i], '" alt="Image ', i, '" onclick="expandImage(this)">\n')

  # Append the generated HTML code to the existing code
  html_code <- paste(html_code, image_html, sep = "")
}

# Close the gallery div
html_code <- paste(html_code, "</div>\n<div class=\"expanded-container\" onclick=\"closeExpanded()\">\n  <img class=\"expanded\" id=\"expanded-image\" onclick=\"navigateGallery(event)\">\n</div>", sep = "")

# Print the final HTML code
cat(html_code)

```{=html}
<!DOCTYPE html>
<html lang="en">
<head>
  <meta charset="UTF-8">
  <meta name="viewport" content="width=device-width, initial-scale=1.0">
  <title>Image Gallery</title>
  <style>
    .gallery {
      display: grid;
      grid-template-columns: repeat(auto-fill, minmax(150px, 1fr));
      grid-gap: 10px;
    }
    .gallery img {
      width: 100%;
      height: 100%;
      object-fit: cover; /* Ensure images cover the entire space */
      cursor: pointer;
      transition: transform 0.3s ease;
    }
    .gallery img:hover {
      transform: scale(1.05); /* Slightly increase size on hover */
    }
    .expanded-container {
      position: fixed;
      top: 0;
      left: 0;
      width: 100%;
      height: 100%;
      background-color: rgba(0, 0, 0, 0.8); /* Semi-transparent background */
      display: none; /* Initially hidden */
      justify-content: center;
      align-items: center;
      z-index: 9999;
    }
    .expanded {
      max-width: 80%;
      max-height: 80%;
      cursor: pointer;
    }
    p.gallery-caption {
      text-align: center;
      font-style: italic;
      color: #8B8989;
    }
  </style>
</head>
<body>

<div class="gallery">
<img src="img/loco-plants/IMG_0064.HEIC" alt="Image 1" onclick="expandImage(this)">
<img src="img/loco-plants/IMG_0820 2.HEIC" alt="Image 2" onclick="expandImage(this)">
<img src="img/loco-plants/IMG_1165.HEIC" alt="Image 3" onclick="expandImage(this)">
<img src="img/loco-plants/IMG_1177.HEIC" alt="Image 4" onclick="expandImage(this)">
<img src="img/loco-plants/IMG_1923.HEIC" alt="Image 5" onclick="expandImage(this)">
</div>
<div class="expanded-container" onclick="closeExpanded()">
  <img class="expanded" id="expanded-image" onclick="navigateGallery(event)">
</div>

<p class="gallery-caption">Greenhouse Volatile Collection Plants looked like this.</p>

<script>
  var currentImageIndex = 0;
  var galleryImages = document.querySelectorAll('.gallery img');

  function expandImage(img) {
    currentImageIndex = Array.from(galleryImages).indexOf(img);
    document.getElementById('expanded-image').src = img.src;
    document.querySelector('.expanded-container').style.display = 'flex';
  }

  function closeExpanded() {
    document.querySelector('.expanded-container').style.display = 'none';
  }

  function navigateGallery(event) {
    // Calculate the click position relative to the expanded image
    var clickX = event.pageX - event.target.getBoundingClientRect().left;
    var imageWidth = event.target.offsetWidth;

    // Determine if the click was on the left or right side of the image
    if (clickX < imageWidth / 2) {
      // Clicked on the left side: navigate to the previous image
      currentImageIndex = (currentImageIndex - 1 + galleryImages.length) % galleryImages.length;
    } else {
      // Clicked on the right side: navigate to the next image
      currentImageIndex = (currentImageIndex + 1) % galleryImages.length;
    }

    // Update the expanded image source
    document.getElementById('expanded-image').src = galleryImages[currentImageIndex].src;
  }
</script>

</body>
</html>

<br>
Volatiles were collected from twleve plants per day using glass volatile collection chambers (VCCs) that were 30 cm long and 4 cm in diameter. The top end of each VCC funneled into a threaded port that was 10 cm in daimter. Threaded onto the top of each VCC was an eight-port "octopus" manifold adapter. Two glass filter traps (6.35 mm diameter x 76 mm length; Analytical Research Systems, Gainesville, FL) with 30 mg of Super-Q absorbent (Alltech Associates, Deerfield, IL) were inserted into two of the adapter ports. The remaining six collection ports were sealed to prevent ambient air exchange and pressure loss. One of the traps was used to collected extraneous volatiles from the initial experiment set up for the first ten minutes, whereas the other trap was used to collect volatile compounds emanating from plants beginning ten minutes after the system was turned on. An air source was connected to the base of each collection chamber with supply from charcoal air filters. A vacuum pump was used to maintain air pressure and flow rate (humidified air at 1.0 liter/min) within the collection system. A small piece of cotton encompassed by a Teflon® guillotine was used at the base of each plant to tightly seal the base of the system and prevent external air from entering. Laboratory tape was used to seal the edges of the guillotine and prevent contamination by ambient and soil derived volatiles.
